A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Prohibtion is 0
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1015 43ef1190-90fd-4dd7-a769-d0121f02b80e
Improve figures
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1016 43ef1190-90fd-4dd7-a769-d0121f02b80e

In Figure~\ref{fig:hardall}\todo{axis and labels}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardall.pdf}}
  \caption{Barplot of all standard-compliant freshness lifetimes
    found. The first bin are the cases where caching is explicitly
    prohibited. The next bins are for lifetimes, where the values are
    grouped if they are on the order of seconds, minutes, hours, etc,
    i.e. the second bin counts the lifetimes in the interval [1,59]
    seconds, etc.}
  \label{fig:hardall}
\end{figure}

@@

\begin{figure}[th!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{heuristicall.pdf}}
  \caption{Barplot of all simple heuristic freshness lifetimes
    found. Bins as in Figure~\ref{fig:hardall}.}
  \label{fig:heuristicall}
\end{figure}

>>>>

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardall.pdf}}
  \caption{Barplot counting all standard-compliant freshness lifetimes
    found, with the percentage of occurances indicated on the
    bars. The first bin are the cases where caching is explicitly
    prohibited. The next bins are for lifetimes, where the values are
    grouped if they are on the order of seconds, minutes, hours, etc,
    i.e. the second bin counts the lifetimes in the interval [1,59]
    seconds, etc.}
  \label{fig:hardall}
\end{figure}

@@

\begin{figure}[th!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{heuristicall.pdf}}
  \caption{Barplot counting all simple heuristic freshness lifetimes
    found. Bins as in Figure~\ref{fig:hardall}.}
  \label{fig:heuristicall}
\end{figure}
